R Notebook

### 2022-04-21 R/HumanDeaminationAnalysis.rmd
Update HumanDeaminationAnalysis.rmd

# Get the tables of read length vs. GC content
CPDReadLengthVsGCData = lapply(CPDMismatchData, function(x) lapply(
  x, getReadLengthAndGCContent
))
sixReadLengthVsGCData = lapply(sixFourMismatchData, function(x) lapply(
  x, getReadLengthAndGCContent
))

@@

```{r plot_position_differences_across_read_lengths, fig.width = 9, fig.height = 5}
plotGroupedPositionStats(CPDGroupedStats$rep1$three_prime, CPDGroupedStats$rep1$five_prime, POS_DIFF,
                         title = "CPD C>T Mismatch Pos Diff Rep1",
                         xAxisBreaks = c(23:31))
plotGroupedPositionStats(CPDGroupedStats$rep2$three_prime, CPDGroupedStats$rep2$five_prime, POS_DIFF,
                         title = "CPD C>T Mismatch Pos Diff Rep2",
                         xAxisBreaks = c(23:31))

@@

# ```{r plot_position_differences_across_read_lengths, fig.width = 9, fig.height = 5}
# plotGroupedPositionStats(CPDGroupedStats$rep1$three_prime, CPDGroupedStats$rep1$five_prime, IQR,
#                          title = "CPD C>T Mismatch Pos Diff Rep1",
#                          xAxisBreaks = c(23:31))
# plotGroupedPositionStats(CPDGroupedStats$rep2$three_prime, CPDGroupedStats$rep2$five_prime, IQR,
#                          title = "CPD C>T Mismatch Pos Diff Rep2",
#                          xAxisBreaks = c(23:31))
# 
# plotGroupedPositionStats(sixFourGroupedStats$rep1$three_prime, sixFourGroupedStats$rep1$five_prime, IQR,
#                          title = "6-4 C>T Mismatch Pos Diff Rep1",
#                          xAxisBreaks = c(23:31))
# plotGroupedPositionStats(sixFourGroupedStats$rep2$three_prime, sixFourGroupedStats$rep2$five_prime, IQR,
#                          title = "6-4 C>T Mismatch Pos Diff Rep2",
#                          xAxisBreaks = c(23:31))
# ```

# ```{r plot_position_differences_across_read_lengths, fig.width = 9, fig.height = 5}
# plotGroupedPositionStats(CPDGroupedStats$rep1$three_prime, CPDGroupedStats$rep1$five_prime, STDEV,
#                          title = "CPD C>T Mismatch Pos Diff Rep1",
#                          xAxisBreaks = c(23:31))
# plotGroupedPositionStats(CPDGroupedStats$rep2$three_prime, CPDGroupedStats$rep2$five_prime, STDEV,
#                          title = "CPD C>T Mismatch Pos Diff Rep2",
#                          xAxisBreaks = c(23:31))
# 
# plotGroupedPositionStats(sixFourGroupedStats$rep1$three_prime, sixFourGroupedStats$rep1$five_prime, STDEV,
#                          title = "6-4 C>T Mismatch Pos Diff Rep1",
#                          xAxisBreaks = c(23:31))
# plotGroupedPositionStats(sixFourGroupedStats$rep2$three_prime, sixFourGroupedStats$rep2$five_prime, STDEV,
#                          title = "6-4 C>T Mismatch Pos Diff Rep2",
#                          xAxisBreaks = c(23:31))
# ```

```{r acquire_and_format_data_2}
# Read in the GC content vs. read length data
CPDReadLengthAndGCFilePaths = list(rep1 = list(), rep2 = list())
CPDReadLengthAndGCFilePaths$rep1 = list(
  hr1 = file.path(deaminationDataDirectory, "NHF1_CPD_1h_Rep1_read_length_vs_GC_content.tsv"),
  hr8 = file.path(deaminationDataDirectory, "NHF1_CPD_8h_Rep1_read_length_vs_GC_content.tsv"),
  hr24 = file.path(deaminationDataDirectory, "NHF1_CPD_24h_Rep1_read_length_vs_GC_content.tsv"),
  hr48 = file.path(deaminationDataDirectory, "NHF1_CPD_48h_Rep1_read_length_vs_GC_content.tsv")
)
CPDReadLengthAndGCFilePaths$rep2 = list(
  hr1 = file.path(deaminationDataDirectory, "NHF1_CPD_1h_Rep2_read_length_vs_GC_content.tsv"),
  hr8 = file.path(deaminationDataDirectory, "NHF1_CPD_8h_Rep2_read_length_vs_GC_content.tsv"),
  hr24 = file.path(deaminationDataDirectory, "NHF1_CPD_24h_Rep2_read_length_vs_GC_content.tsv"),
  hr48 = file.path(deaminationDataDirectory, "NHF1_CPD_48h_Rep2_read_length_vs_GC_content.tsv")
)

sixFourReadLengthAndGCFilePaths = list(rep1 = list(), rep2 = list())
sixFourReadLengthAndGCFilePaths$rep1 = list(
  min5 = file.path(deaminationDataDirectory, "NHF1_6-4-PP_5min_Rep1_read_length_vs_GC_content.tsv"),
  min20 = file.path(deaminationDataDirectory, "NHF1_6-4-PP_20min_Rep1_read_length_vs_GC_content.tsv"),
  hr1 = file.path(deaminationDataDirectory, "NHF1_6-4-PP_1h_Rep1_read_length_vs_GC_content.tsv")
)
sixFourReadLengthAndGCFilePaths$rep2 = list(
  min5 = file.path(deaminationDataDirectory, "NHF1_6-4-PP_5min_Rep2_read_length_vs_GC_content.tsv"),
  min20 = file.path(deaminationDataDirectory, "NHF1_6-4-PP_20min_Rep2_read_length_vs_GC_content.tsv"),
  hr1 = file.path(deaminationDataDirectory, "NHF1_6-4-PP_1h_Rep2_read_length_vs_GC_content.tsv")
)

CPDReadLengthAndGCData = lapply(CPDReadLengthAndGCFilePaths, function(x) lapply(x, fread))
sixFourReadLengthAndGCData = lapply(sixFourReadLengthAndGCFilePaths, function(x) lapply(x, fread))
```

```{r CPD_read_length_vs_GC_content}
for (i in 1:length(CPDReadLengthAndGCData)) {
  for (j in 1:length(CPDReadLengthAndGCData[[i]])) {
    plotGCContentVsReadLength(CPDReadLengthAndGCData[[i]][[j]],
                              title = paste("CPD", names(CPDReadLengthAndGCData)[i], 
                                            names(CPDReadLengthAndGCData[[i]])[j], "GC Content Vs Read Length"))
  }
}
```

```{r 6-4_read_length_vs_GC_content}
for (i in 1:length(sixFourReadLengthAndGCData)) {
  for (j in 1:length(sixFourReadLengthAndGCData[[i]])) {
    plotGCContentVsReadLength(sixFourReadLengthAndGCData[[i]][[j]],
                              title = paste("6-4", names(sixFourReadLengthAndGCData)[i], 
                                            names(sixFourReadLengthAndGCData[[i]])[j], "GC Content Vs Read Length"))
  }
}
```

@@

```{r acquire_and_format_data_3}
load(file.path(deaminationDataDirectory, "NHF1_TCG_deamination_periodicity_results.rda"))
dataSetNames = as.list(setNames(nm = mutperiodData$periodicityResults$Data_Set))

>>>>

# # Get the tables of read length vs. GC content
# CPDReadLengthVsGCData = lapply(CPDMismatchData, function(x) lapply(
#   x, getReadLengthAndGCContent
# ))
# sixReadLengthVsGCData = lapply(sixFourMismatchData, function(x) lapply(
#   x, getReadLengthAndGCContent
# ))

@@

```{r position_differences_across_read_lengths, fig.width = 9, fig.height = 5}
plotGroupedPositionStats(CPDGroupedStats$rep1$three_prime, CPDGroupedStats$rep1$five_prime, POS_DIFF,
                         title = "CPD C>T Mismatch Pos Diff Rep1",
                         xAxisBreaks = c(23:31))
plotGroupedPositionStats(CPDGroupedStats$rep2$three_prime, CPDGroupedStats$rep2$five_prime, POS_DIFF,
                         title = "CPD C>T Mismatch Pos Diff Rep2",
                         xAxisBreaks = c(23:31))

@@

# ```{r plot_stats_across_read_lengths, fig.width = 9, fig.height = 5}
# plotGroupedPositionStats(CPDGroupedStats$rep1$three_prime, CPDGroupedStats$rep1$five_prime, IQR,
#                          title = "CPD C>T Mismatch Pos Diff Rep1",
#                          xAxisBreaks = c(23:31))
# plotGroupedPositionStats(CPDGroupedStats$rep2$three_prime, CPDGroupedStats$rep2$five_prime, IQR,
#                          title = "CPD C>T Mismatch Pos Diff Rep2",
#                          xAxisBreaks = c(23:31))
# 
# plotGroupedPositionStats(sixFourGroupedStats$rep1$three_prime, sixFourGroupedStats$rep1$five_prime, IQR,
#                          title = "6-4 C>T Mismatch Pos Diff Rep1",
#                          xAxisBreaks = c(23:31))
# plotGroupedPositionStats(sixFourGroupedStats$rep2$three_prime, sixFourGroupedStats$rep2$five_prime, IQR,
#                          title = "6-4 C>T Mismatch Pos Diff Rep2",
#                          xAxisBreaks = c(23:31))
# ```

```{r purine_vs_pyrimidine_frequencies_across_read_length, fig.width = 11, fig.height = 5}

plotNucFreqVsReadLengthBarPlot(CPDSingleCToTMismatchData$rep1, THREE_PRIME,
                               title = "CPD Rep1 3' Nuc Freq",
                               combineNucleotides = c("AG","CG"), combinedNames = c("Purine","Pyrimidine"))
plotNucFreqVsReadLengthBarPlot(CPDSingleCToTMismatchData$rep2, THREE_PRIME,
                               title = "CPD Rep2 3' Nuc Freq",
                               combineNucleotides = c("AG","CG"), combinedNames = c("Purine","Pyrimidine"))
plotNucFreqVsReadLengthBarPlot(CPDSingleCToTMismatchData$rep1, FIVE_PRIME,
                               title = "CPD Rep1 5' Nuc Freq",
                               combineNucleotides = c("AG","CG"), combinedNames = c("Purine","Pyrimidine"))
plotNucFreqVsReadLengthBarPlot(CPDSingleCToTMismatchData$rep2, FIVE_PRIME,
                               title = "CPD Rep2 5' Nuc Freq",
                               combineNucleotides = c("AG","CG"), combinedNames = c("Purine","Pyrimidine"))

plotNucFreqVsReadLengthBarPlot(sixFourSingleCToTMismatchData$rep1, THREE_PRIME,
                               title = "6-4 Rep1 3' Nuc Freq",
                               combineNucleotides = c("AG","CG"), combinedNames = c("Purine","Pyrimidine"))
plotNucFreqVsReadLengthBarPlot(sixFourSingleCToTMismatchData$rep2, THREE_PRIME,
                               title = "6-4 Rep2 3' Nuc Freq",
                               combineNucleotides = c("AG","CG"), combinedNames = c("Purine","Pyrimidine"))
plotNucFreqVsReadLengthBarPlot(sixFourSingleCToTMismatchData$rep1, FIVE_PRIME,
                               title = "6-4 Rep1 5' Nuc Freq",
                               combineNucleotides = c("AG","CG"), combinedNames = c("Purine","Pyrimidine"))
plotNucFreqVsReadLengthBarPlot(sixFourSingleCToTMismatchData$rep2, FIVE_PRIME,
                               title = "6-4 Rep2 5' Nuc Freq",
                               combineNucleotides = c("AG","CG"), combinedNames = c("Purine","Pyrimidine"))

# ```{r acquire_and_format_data_2}
# # Read in the GC content vs. read length data
# CPDReadLengthAndGCFilePaths = list(rep1 = list(), rep2 = list())
# CPDReadLengthAndGCFilePaths$rep1 = list(
#   hr1 = file.path(deaminationDataDirectory, "NHF1_CPD_1h_Rep1_read_length_vs_GC_content.tsv"),
#   hr8 = file.path(deaminationDataDirectory, "NHF1_CPD_8h_Rep1_read_length_vs_GC_content.tsv"),
#   hr24 = file.path(deaminationDataDirectory, "NHF1_CPD_24h_Rep1_read_length_vs_GC_content.tsv"),
#   hr48 = file.path(deaminationDataDirectory, "NHF1_CPD_48h_Rep1_read_length_vs_GC_content.tsv")
# )
# CPDReadLengthAndGCFilePaths$rep2 = list(
#   hr1 = file.path(deaminationDataDirectory, "NHF1_CPD_1h_Rep2_read_length_vs_GC_content.tsv"),
#   hr8 = file.path(deaminationDataDirectory, "NHF1_CPD_8h_Rep2_read_length_vs_GC_content.tsv"),
#   hr24 = file.path(deaminationDataDirectory, "NHF1_CPD_24h_Rep2_read_length_vs_GC_content.tsv"),
#   hr48 = file.path(deaminationDataDirectory, "NHF1_CPD_48h_Rep2_read_length_vs_GC_content.tsv")
# )
# 
# sixFourReadLengthAndGCFilePaths = list(rep1 = list(), rep2 = list())
# sixFourReadLengthAndGCFilePaths$rep1 = list(
#   min5 = file.path(deaminationDataDirectory, "NHF1_6-4-PP_5min_Rep1_read_length_vs_GC_content.tsv"),
#   min20 = file.path(deaminationDataDirectory, "NHF1_6-4-PP_20min_Rep1_read_length_vs_GC_content.tsv"),
#   hr1 = file.path(deaminationDataDirectory, "NHF1_6-4-PP_1h_Rep1_read_length_vs_GC_content.tsv")
# )
# sixFourReadLengthAndGCFilePaths$rep2 = list(
#   min5 = file.path(deaminationDataDirectory, "NHF1_6-4-PP_5min_Rep2_read_length_vs_GC_content.tsv"),
#   min20 = file.path(deaminationDataDirectory, "NHF1_6-4-PP_20min_Rep2_read_length_vs_GC_content.tsv"),
#   hr1 = file.path(deaminationDataDirectory, "NHF1_6-4-PP_1h_Rep2_read_length_vs_GC_content.tsv")
# )
# 
# CPDReadLengthAndGCData = lapply(CPDReadLengthAndGCFilePaths, function(x) lapply(x, fread))
# sixFourReadLengthAndGCData = lapply(sixFourReadLengthAndGCFilePaths, function(x) lapply(x, fread))
# ```

# ```{r CPD_read_length_vs_GC_content}
# for (i in 1:length(CPDReadLengthAndGCData)) {
#   for (j in 1:length(CPDReadLengthAndGCData[[i]])) {
#     plotGCContentVsReadLength(CPDReadLengthAndGCData[[i]][[j]],
#                               title = paste("CPD", names(CPDReadLengthAndGCData)[i], 
#                                             names(CPDReadLengthAndGCData[[i]])[j], "GC Content Vs Read Length"))
#   }
# }
# ```
# 
# 
# ```{r 6-4_read_length_vs_GC_content}
# for (i in 1:length(sixFourReadLengthAndGCData)) {
#   for (j in 1:length(sixFourReadLengthAndGCData[[i]])) {
#     plotGCContentVsReadLength(sixFourReadLengthAndGCData[[i]][[j]],
#                               title = paste("6-4", names(sixFourReadLengthAndGCData)[i], 
#                                             names(sixFourReadLengthAndGCData[[i]])[j], "GC Content Vs Read Length"))
#   }
# }
# ```

@@

```{r acquire_and_format_data_4}
load(file.path(deaminationDataDirectory, "NHF1_TCG_deamination_periodicity_results.rda"))
dataSetNames = as.list(setNames(nm = mutperiodData$periodicityResults$Data_Set))
